Cover letter for the original IJRR submission

### 2017-10-09 body/equilibrium.tex
equality between dual and primal optimum
nicolas comments

We observe that if $b_0$ is positive then \eqref{eq:lin_prog} admits a solution, and $b_0$ is proportional to the minimum distance of the contact forces to the boundaries of the friction cones.
If $b_0$ is negative, the configuration is not in static equilibrium, and $b_0$ indicates ``how far'' from equilibrium the configuration is. We thus use $b_0$ as a measure of robustness.

In our implementation, rather than solving directly \eqref{eq:lin_prog_rob}, we solve an equivalent problem of smaller dimension that we get by taking the dual of \eqref{eq:lin_prog_rob} and eliminating the Lagrange multipliers associated to the inequality constraints:
\begin{equation} \label{eq:dual} \begin{aligned}
\find \quad & \bm{\nu} \in \Rv{6}\\
\maximize  \quad & -(\mathbf{D} \mathbf{c} + \mathbf{d})^T \nu \\
\st \quad &\mathbf{G}^T \bm{\nu} \ge 0 \\
& \mathbf{1}^T \mathbf{G}^T \bm{\nu} = 1 \\
\end{aligned} \end{equation}

Indeed, from Slater's conditions \citep{Boyd:2004:CO:993483}, we know that the optimal values of an LP and its dual are equal. Thus the optimal value of the LP~\eqref{eq:dual} is indeed the optimal $b_0$.

>>>>

We observe that if $b_0$ is positive then \eqref{eq:lin_prog} admits a solution, and $b_0$ is proportional to the minimum distance of the contact forces to the boundaries of the friction cones.
If $b_0$ is negative, the configuration is not in static equilibrium, and $b_0$ indicates ``how far'' from equilibrium the configuration is. We thus use $b_0$ as a measure of robustness.
%~ One advantage of $b_0$ is that it gives a constant margin 
A simple approach to robustness consists in choosing a smaller friction coefficient, to constrain the forces to lie away from the boundaries of the real cone.  However, this would result in a small safety margin for forces of low magnitude, and an excessively big safety margin for large forces as the boundaries grow more and more appart. In comparison, our margin $b_0$ is constant, and provides a helpful mean to compare the robustness of different contact configurations.

In our implementation, rather than solving directly \eqref{eq:lin_prog_rob}, we solve an equivalent problem of smaller dimension that we get by taking the dual of \eqref{eq:lin_prog_rob} and eliminating the Lagrange multipliers associated to the inequality constraints:
\begin{equation} \label{eq:dual} \begin{aligned}
\find \quad & \bm{\nu} \in \Rv{6}\\
\maximize  \quad & -(\mathbf{D} \mathbf{c} + \mathbf{d})^T \bm{\nu} \\
\st \quad &\mathbf{G}^T \bm{\nu} \ge 0 \\
& \mathbf{1}^T \mathbf{G}^T \bm{\nu} = 1 \\
\end{aligned} \end{equation}

Indeed, from Slater's conditions \citep{Boyd:2004:CO:993483}, we know that the optimal values of an LP and its dual are equal.
Therefore the optimal value $\bm{\nu}^*$ gives the optimal value $b_0^*$ through the equality $b_0^* = (\mathbf{D} \mathbf{c} + \mathbf{d})^T \bm{\nu}^*$.
 %~ Thus the optimal value of the LP~\eqref{eq:dual} is indeed the optimal $b_0$.
